### 2023-06-12 manuscript.tex
40 pages! [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/76ebc8f6ebdf030e2b62b590e21331952649784f.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/76ebc8f6ebdf030e2b62b590e21331952649784f/checks
https://github.com/stain/2022-fdo-paper/actions/runs/5248371671

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/fe73d9fbfc49fdc4a9fc913c0ccd95c6b0ef7ab3}{stain/2022-fdo-paper@fe73d9f}
on June 12, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/76ebc8f6ebdf030e2b62b590e21331952649784f/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/76ebc8f6ebdf030e2b62b590e21331952649784f}{stain/2022-fdo-paper@76ebc8f}
on June 12, 2023.
